\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\section{Demo Plans}

For the demo, we plan to walk through the main success case for a user using the application.
The demo will start with logging in using an existing account, before scanning a receipt. Once
the receipt is scanned, we will show how the confirmation screen looks. We will show how editing
data on the confirmation screen works before sending the data to the backend. Once everything has
been properly added to the database, the analytics screen will be accessed to display the account's
purchase history and data. Finally, we will show how recommendations would be received for a user
using the application.

\section{Meeting Attendance}

\wss{For each team member how many team meetings have they attended since the
POC demo.  This number should be determined from the meeting issues in the
team's repo.  The first entry in the table should be the total number of team
meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 13\\
Ryan Yeh & 13\\
Allan Fang & 13\\
Name 3 & Num\\
Name 4 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended since the POC
demo.  This number should be determined from the lecture issues in the team's
repo.  The first entry in the table should be the total number of lectures since
the POC demo.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Ryan Yeh & 2\\
Allan Fang & 1\\
Name 3 & Num\\
Name 4 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
since the POC demo.  The total is the total number of commits for the entire
team since the POC demo.  The percentage is the percentage of the total commits
made by each team member.}

The below contains the number of commits made by team members across all our repositories. This includes
contributions to the main repository as well as sub-repositories that make up our actual implementation.

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 117 & 100\% \\
Ryan Yeh & 60 & 51.28\% \\
Allan Fang & 13 & 11.11\% \\
Name 3 & Num & \% \\
Name 4 & Num & \% \\
\bottomrule
\end{tabular}
\end{table}

\begin{itemize}
  \item \textbf{Ryan Yeh:} I have an additional 45 commits made to our frontend repository that has not yet been
  merged to the main branch since the feature is still under development. I would also like to note that I write
  documentation on a local \LaTeX environment rather than Overleaf so I am generally able to make much more commits.
  \item \textbf{Allan Fang:} I have an additional 5 pending commits that are not ready for the main branch as the feature is incomplete.
  \item \textbf{Sawyer Tang:}
  \item \textbf{Jason Nam:}
\end{itemize}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues) and how many have they been assigned (only counting closed
issues).}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ryan Yeh & 54 & 36 \\
Allan Fang & 40 & 29 \\
Name 3 & Num & Num \\
Name 4 & Num & Num \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{CICD}

Currently, \textit{Github Actions} is being used to compile all of our \LaTeX documents in the primary repository.
Going forward, we aim to have unit tests being executed when merging branches as well in order to ensure code quality.
Once modules are more complete, these tests will be created and integrated in to the CICD pipeline.

\end{document}